R Notebook

### 2023-04-29 02_paper/02_study/02_fitbit paper/analysis_270423.Rmd
jgsldjf

fit_pre_1 <-
  df_multi %>% 
  filter(Phase == "Pre Teaching Phase") %$% 
  lm(slope ~ disruption)

fit_pre_2 <-
  df_multi %>% 
  filter(Phase == "Pre Teaching Phase") %$% 
  lm(slope ~ confidence)

fit_pre_3 <-
  df_multi %>% 
  filter(Phase == "Pre Teaching Phase") %$% 
  lm(slope ~ teaching_experience)

fit_pre_4 <-
  df_multi %>% 
  filter(Phase == "Pre Teaching Phase") %$% 
  lm(slope ~ confidence + disruption)

fit_pre_5 <-
  df_multi %>% 
  filter(Phase == "Pre Teaching Phase") %$% 
  lm(slope ~ confidence + disruption + teaching_experience)

stargazer::stargazer(fit_pre_1, fit_pre_2,fit_pre_3, fit_pre_4, fit_pre_5,
                     type = "latex",
                     caption = "Pre Teaching Phase",
                     dep.var.labels = "Slope",
                     order = c(1, 2, 3),
                     covariate.labels = c("Disruption Factor",
                                          "Confidence Factor",
                                          "Teaching Experience"),
                     keep.stat = c("n","rsq","adj.rsq")
                     )
```

@@

fit_post_1 <-
  df_multi %>% 
  filter(Phase == "Post Teaching Phase") %$% 
  lm(slope ~ disruption)

>>>>

```{r}
df_multi <- 
  main %>% 
  select("ID", "disruption_factor", "confidence_factor", "teaching_experience") %>% 
  distinct() %>% 
  group_by(ID) %>% 
  summarize(disruption = mean(disruption_factor, na.rm = T),
            confidence = mean(confidence_factor, na.rm = T),
            teaching_experience) %>% 
  ungroup() %>% 
  mutate(id = as.character(ID)) %>% 
  distinct() %>% 
  right_join(x = .,
            y = fix_models,
            by = "id") %>% 
  mutate(posneg = if_else(condition = slope < 0,
                          true = "negative",
                          false = "positive"))

fit_pre_1 <-
  df_multi %>% 
  filter(Phase == "Pre Teaching Phase") %$% 
  lm(slope ~ disruption * posneg)

fit_pre_2 <-
  df_multi %>% 
  filter(Phase == "Pre Teaching Phase") %$% 
  lm(slope ~ confidence:posneg)

fit_pre_3 <-
  df_multi %>% 
  mutate(teaching_experience = log(teaching_experience + 1)) %>% 
  filter(Phase == "Pre Teaching Phase") %$% 
  lm(slope ~ teaching_experience:posneg)

fit_pre_4 <-
  df_multi %>% 
  filter(Phase == "Pre Teaching Phase") %$% 
  lm(slope ~ confidence:posneg + disruption:posneg)

fit_pre_5 <-
  df_multi %>% 
  filter(Phase == "Pre Teaching Phase") %$% 
  lm(slope ~ posneg:confidence + posneg:disruption + posneg:teaching_experience)

stargazer::stargazer(fit_pre_1, fit_pre_2,fit_pre_3, fit_pre_4, fit_pre_5,
                     type = "latex",
                     caption = "Pre Teaching Phase",
                     dep.var.labels = "Slope",
                     # order = c(1, 2, 3),
                     # covariate.labels = c("Disruption Factor",
                     #                      "Confidence Factor",
                     #                      "Teaching Experience"),
                     keep.stat = c("n","rsq","adj.rsq")
                     )

fit_pre_3$model %>%
  mutate(fitted.values = fit_pre_3$fitted.values) %>% 
  ggplot(mapping = aes(x = teaching_experience,
                       y = slope
                       )
         ) +
  geom_point(mapping = aes(group = posneg)) +
          geom_line(mapping = aes(y = fitted.values,
                                  group = posneg)) +
  geom_smooth(method = "lm",
              se = F,
              linetype = "dashed") +
        # geom_point(alpha = 0.5,
        #            size = 0.5) +
        theme_apa()

@@

fit_post_1 <-
  df_multi %>% 
  filter(Phase == "Post Teaching Phase") %>% 
  split(.$posneg) %>% 
  map(~ lm(slope ~ disruption,
           data = .))

df_multi %>% 
  filter(Phase == "Post Teaching Phase") %$% 
  lm(slope ~ disruption:posneg)
